### 2022-07-28 doc/university-covid.tex
updating

\begin{flushleft}{
	\Large
	\textbf\newline{
		Relative role of community transmission and campus contagion in driving the spread of SARS-CoV-2: lessons from Princeton University
	}
}
\newline
\\
Sang Woo Park\textsuperscript{1}
Irini Daskalaki\textsuperscript{2}
Robin M. Izzo\textsuperscript{3}
Irina Aranovich\textsuperscript{4}
Aartjan J.W. te Velthuis\textsuperscript{4}
Daniel A. Notterman\textsuperscript{4}
C. Jessica E. Metcalf\textsuperscript{1}
Bryan T.\ Grenfell\textsuperscript{1,5}
\\
\bigskip
\textbf{1} Department of Ecology and Evolutionary Biology, Princeton University, Princeton, NJ, USA
\\
\textbf{2} University Health Services, Princeton University, Princeton, NJ, USA
\\
\textbf{3} Environmental Health and Safety, Princeton University, Princeton, NJ, USA
\\
\textbf{4} Department of Molecular Biology, Princeton University, Princeton, NJ, USA
\\
\textbf{5} Princeton School of Public and International Affairs, Princeton University, Princeton, NJ, USA
\\
\bigskip

@@

>>>>

\begin{flushleft}{
	\Large
	\textbf\newline{
		Relative role of community transmission and campus contagion in driving the spread of SARS-CoV-2: lessons from Princeton University
	}
}
\newline
\\
Sang Woo Park\textsuperscript{1}
Irini Daskalaki\textsuperscript{2}
Robin M. Izzo\textsuperscript{3}
Irina Aranovich\textsuperscript{4}
Aartjan J.W. te Velthuis\textsuperscript{5}
Daniel A. Notterman\textsuperscript{5}
C. Jessica E. Metcalf\textsuperscript{1}
Bryan T.\ Grenfell\textsuperscript{1,6}
\\
\bigskip
\textbf{1} Department of Ecology and Evolutionary Biology, Princeton University, Princeton, NJ, USA
\\
\textbf{2} University Health Services, Princeton University, Princeton, NJ, USA
\\
\textbf{3} Environmental Health and Safety, Princeton University, Princeton, NJ, USA
\\
\textbf{4} Princeton University Clinical Laboratory, Princeton University, Princeton, NJ, USA
\\
\textbf{5} Department of Molecular Biology, Princeton University, Princeton, NJ, USA
\\
\textbf{6} Princeton School of Public and International Affairs, Princeton University, Princeton, NJ, USA
\\
\bigskip

@@

\section*{Data availability}

All data and code are stored in a publicly available GitHub repository (\url{https://github.com/parksw3/university-covid}).
